---
title: "Lab 07 - Modelling course evaluations"
author: "Annie O'Dell"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
view(evals)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
evals %>%
  ggplot(mapping = aes(x = score))+
  geom_bar()

evals %>% 
  group_by(gender) %>%
  summarise(mean_score = mean(score),
            max_score = max(score),
            min_score = min(score),
            med_score = median(score))
```
exercise 1: the bar chart shows a left skew, indicating that students generally rate courses with a more positive outlooks (hence higher scores). Comparing genders, both females and males rate the courses rather consistently with females giving just a slightly higher score on average.

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
evals %>%
  ggplot(mapping = aes( x = score, y = bty_avg)) +
  geom_point()

evals %>%
  ggplot(mapping = aes( x = score, y = bty_avg)) +
  geom_jitter()
```
Jitter adds a small amount of random variation to the location of each point. The first point graph makes the data look more uniform and struggles to show the datas correlation.

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

score = 3.88 + 0.067*bty_avg. it could make sense but not really

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
evals %>%
  ggplot(mapping = aes( x = score, y = bty_avg)) +
  geom_jitter() +
  geom_smooth(method = lm)
```

3. Interpret the slope of the linear model in context of the data.

as the beauty rating increases, the scores generally increase

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

it doesn't make sense in the context of the data as it is implying that the lowest beauty possible isn't 0, therefore the lowest score cant be 0 which makes the range wrong.

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$r.squared
```

*Add your interpretation here*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

score_bty_aug %>%
  ggplot(mapping = aes(x = .fitted, y = .resid)) +
  geom_jitter() + 
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  geom_smooth(method = lm)
  
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
evals %>%
  count(rank)
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
score_rank_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ rank, data = evals)

tidy(score_rank_fit)
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
score_gender_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ gender, data = evals)

tidy(score_gender_fit)
```

```{r score_gender_intercept}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

The intercept of the model is `r score_gender_intercept`
The intercept of the model is `r round(score_gender_intercept, 2)`

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
